Global Climate and Atmosphere Composition of the Ultra-Hot Jupiter WASP-103\lowercase{b} from \HST\ and Spitzer Phase Curve Observations

### 2017-12-18 ms.tex
retrieval results

@@

\section{Atmospheric Composition}
Since the phase-resolved spectra are consistent with blackbodies (except for the Spitzer 4.5 $\mu$m broadband photometry point), we opted for a simple grid-based retrieval of the planet's atmospheric properties, similar to the grid search used in Mansfield et al. and Arcangeli et al. (in prep). We generated a grid from one-dimensional forward models of the atmosphere over a broad range of metallicities, carbon-to-oxygen ratios (C/O), and stellar irradiation (\textbf{Mike: elaborate}). The forward models compute self-consistent, radiative-convective temperature-pressure (T-P) profiles, and the molecular abundances are calculated in each atmospheric layer assuming thermochemical equilibrium.  We included opacity from the major absorbers expected for a hot Jupiter atmosphere (FIXME: Mike, what molecules are included?). Notably, in contrast to many previous studies of the hottest planets, we also included opacity from H-, which is expected because water dissociates (FIXME: what temperatures?).  We Using these opacities and T-P profiles, we calculated thermal emission spectra over the full grid using the CHIMERA retrieval suite.  We then explored the grid with an MCMC chain using the \texttt{emcee} package \citep{foremanmackey13} (FIXME: elaborate).

The best fit atmospheric metallicity is FIXME and 
The 68\% confidence interval for a

When we do not include H- opacity, FIXME what happens?

>>>>

Over the WFC3 bandpass, the phase-resolved spectra are featureless and consistent with blackbodies (with best fit $\chi^2_\nu$ ranging from $0.5-1.3$). However, the \Spitzer\ data, particularly at 4.5 $\mu$m, are discrepant with the best fit blackbody by $3-5\,\sigma$ at most orbital phases, indicating the presence of infrared molecular absorption or emission features. We investigate possible atmospheric compositions and temperature structures in \S\,\ref{sec:composition}.

@@

\subsection{Clouds?}

\section{Retrieved Atmospheric Composition and Thermal Structure}
\label{sec:composition}
Since the phase-resolved spectra do not show spectrally resolved molecular features, we opted for a simple grid-based retrieval of the planet's atmospheric properties, similar to the grid search used in Mansfield et al. and Arcangeli et al. (in prep). We generated a grid from one-dimensional forward models of the atmosphere over a broad range of metallicities, carbon-to-oxygen ratios (C/O), and stellar irradiation (\textbf{Mike: elaborate}). The forward models compute self-consistent, radiative-convective temperature-pressure (T-P) profiles, and the molecular abundances are calculated in each atmospheric layer assuming thermochemical equilibrium.  We included opacity from the major absorbers expected for a hot Jupiter atmosphere, including H$_2$O, CO, CO$_2$, TiO, and VO (\textbf{Mike: what others?}). Notably, in contrast to many previous studies of the hottest planets, we also included opacity from H-, which is expected because water dissociates at temperatures .  Using these opacities and T-P profiles, we calculated thermal emission spectra over the full grid using the CHIMERA retrieval suite.  We then explored the grid with an MCMC chain using the \texttt{emcee} package \citep{foremanmackey13}, and interpolated in the grid to calculate the likelihood at each model step. We retrieved the composition for dayside emission spectrum and at FIXME phases

\subsection{Dayside}
We show the retrieved metallicity and C/O in Figure\,\ref{fig:composition}. The best fit metallicity is $23^{+29}_{-13}\times$ solar, somewhat higher than expected based on Jupiter's metal enrichment \citep[$3-5\times$ solar][]{wong04} and the trend toward decreasing metallicity with increasing planet mass observed for the Solar System and exoplanets \cite[e.g.][]{kreidberg14}.  However, planet population synthesis models predict some scatter in atmospheric metallicity. Planets near WASP-103b's mass ($1.5\,M_\mathrm{Jup}$) are expected to have metallicities ranging from $1-10\times$ solar \citep{mordasini16}. Our result for WASP-103b lies on the upper end of this range, and may be indicative of intrinsic scatter in the mass-atmospheric metallicity relation.

The retrieved C/O is consistent with solar, with a $1\sigma$ confidence interval of $0.54 - 0.85$. We infer an upper limit on C/O of 0.9 at $3\,\sigma$ confidence, driven by the fact that the atmospheric chemistry is expected to change dramatically when C/O exceeds unity. For a carbon-rich composition, the equilibrium abundance of methane relative to CO increases by orders of magnitude compared to an oxygen-rich  composition \citep[e.g.][]{madhusudhan11}. The \Spitzer\ eclipse depths are sensitive to the relative abundance of these species, so we can confidently rule out a carbon-rich composition in spite of the lack of spectrally resolved features.  
Thermal structure.

We note that an important caveat for our results is that the best fit model is not a perfect fit to the data (with $\chi_\nu = 1.77$), so the uncertainties produced by the MCMC may be underestimated. Furthermore, the inferred C/O and metallicity are highly sensitive to the large planet-to-star flux at \Spitzer $4.5\mu$m, which is the worst fit data point. (With this point removed, the fit quality is significantly improved: $\chi_\nu = 1.17$).  The dominant absorbing species over the $4.5\,\mu$m bandpass is CO, so to fit this point the model tends to favor super-solar metallicities and C/O. Given that the result is driven by a single photometric band and there are no resolved molecular features to constrain the absorbers that are present or the temperature-pressure profile, we caution against over-interpreting these results until wider spectral coverage is available.

Figure\,\ref{fig:TP} shows the retrieved temperature pressure profiles for the dayside. They exhibit a

As a test of our modeling approach, we also performed a retrieval in which the T/P profile was allowed to vary. 
No H- ?

\subsection{Other Orbital Phases}
We also modeled the
